{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-23 paper/paper.tex
explained second rule
added explanation of execution rule three

>>>>

The second rule covers the case in which the thread pickted by the scheduler has only the current
instruction before terminating (i.e. $\simga.pc = \mathtt{exit}$). In the concurrent transition
the current thread id is removed from the concurrent state and everything else is like in the
first rule.

The third rule introduces the dynamic creation of new threads. In this rule the function $fresh_{l}$
takes a set of thread identifiers and returns a new thread identifier at level $l$\footnote{It is
assumed that $fresh_l \neq fresh_{l'} Leftrightarrow l \neq l'$} and $\lambda_{init} : \mathcal{P}
\rightarrow LocState$ produces an initial state with the program pointer at the given program point.
If the current instruction at program point $i$ is the \texttt{start} instruction, a new thread
identifier is pickt w.r.t. the security level of $i$. The program counter of the current thread
is increased by one, to step to the next instruction. The resulting concurrent state includes the
updated state of the current thread and the initial state for the new thread. The global memory
is not modified and the history is extended with the current thread id and the security level of $i$.
